COG-ED Manuscript

### 2021-11-25 06_Paper/COG-ED/Manuscript.Rmd
added sentence to intro

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

@@

## Effort discounting and Need for Cognition 
The individual degree of ED in the study by Westbrook et al. [-@Westbrook2013] was also associated with the participants' Need for Cognition (NFC) score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
Westbrook et al. [-@Westbrook2013] conceptualized NFC as a subjective self-report of ED for each participant which could then be related to the SVs as an objective measure.
On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
However, the relation of NFC and SVs might be confounded, since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance [@Kramer2021] or found no association of NFC and SVs at all [@Crawford2021].
On the other hand, task load has been shown to be a better predictor of SVs than task performance [@Culbreth2016; @Westbrook2013; @Westbrook2019], so more research is needed to shed light on this issue.

>>>>

abstract: |
  Every day, individuals have to weigh the value of the reward when reaching a goal against the required effort.
  However, effort is not inherently aversive to all individuals, which has often been neglected by previous approaches to quantify the subjective value of effort.
  One of them is the Cognitive Effort Discounting paradigm by Westbrook et al. (2013), which can quantify the subjective values of the difficult levels of the n-back task against the easiest level.
  We argue that adapting the paradigm and the method of computing the willingness to exert effort allows two crucial things: Quantifying subjective values without assuming that the easiest level is preferred, and quantifying subjective values for tasks with no objective order of task load.
  We aim to replicate the analysis of Westbrook et al. (2013) with our adaptation, the Cognitive and Emotion Regulation Effort Discounting paradigm (CERED).

@@

## Effort discounting and Need for Cognition 
The individual degree of ED in the study by Westbrook et al. [-@Westbrook2013] was also associated with the participants' Need for Cognition (NFC) score, a personality trait describing individuals who actively seek and enjoy effortful cognitive activities [@Cacioppo1982].
Westbrook et al. [-@Westbrook2013] conceptualized NFC as a subjective self-report of ED for each participant which could then be related to the SVs as an objective measure.
On the surface, this association stands to reason, as individuals with higher NFC are more motivated to mobilize cognitive effort because they perceive it as intrinsically rewarding.
Additionally, it has been shown that individuals avoid cognitive effort only to a certain degree, possibly to retain a sense of self-control [@Wu2021], a trait more prominent in individuals with high NFC [@Bertrams2012; @Nishiguchi2016; Xu2021].
However, the relation of NFC and SVs might be confounded, since other studies utilizing the COG-ED paradigm found the association of NFC and SVs to disappear after correcting for performance [@Kramer2021] or found no association of NFC and SVs at all [@Crawford2021].
On the other hand, task load has been shown to be a better predictor of SVs than task performance [@Culbreth2016; @Westbrook2013; @Westbrook2019], so more research is needed to shed light on this issue.
